Future challenges for Research Software Engineering

### 2025-04-14 future_challenges_for_RSEng.tex
Update future_challenges_for_RSEng.tex
Co-authored-by: Jan Philipp Thiele <54978337+jpthiele@users.noreply.github.com>
work in feedback

\subsection{How have academic Institutions transformed by then? ( Point 4 in the issue )}
\subsubsection{What do we want to have achieved}
We hope to see that universities use the presence of an RSE Department actively as a means to differentiate themselves from other universities.
We also hope, that specialized clusters form, with certain RSE units specializing in certain tasks like data management, HPC, or visualization.
At universities which have them, we want to see, that researchers naturally accept them as part of their used services.

@@

What are open questions here?
Organizations will have to come up with models for hiring people. While
a standardized RSE masters makes it easier, it will be interesting to see, if
RSE are still often hired inhouse or if it changes.

>>>>

\subsection{How have academic Institutions transformed by then? ( Point 4 in the issue )}
\subsubsection{What do we want to have achieved}
We hope to see that universities use the presence of an RSE Department actively as a means to differentiate themselves from other universities.
We hope that the central RSE units have local RSE representatives, or even small RSE groups that handle tasks within a department to oversee specific projects[FIXME: cite group paper].
We also hope, that specialized clusters form, with certain RSE units specializing in certain tasks like data management, HPC, or visualization.
At universities which have them, we want to see, that researchers naturally accept them as part of their used services.

@@

What are open questions here?
Organizations will have to come up with models for hiring people. While
a standardized RSE masters makes it easier, it will be interesting to see, if
RSE are still often hired by word of mouth or if the master's really makes it more comparable.
